\documentclass{report}
\usepackage{subfiles}
\usepackage[latin1]{inputenc}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{float}
\usepackage{color}



\fancyfoot[OC]{\textit{\thepage}}

\title{Sample Title}
\date{\today}
\author{Asbj\o rn Fjelbro Steffensen (afjs@itu.dk)\\ Thomas Stoy Dragsb\ae k (thst@itu.dk)\\ Nicki Hjorth J\o rgensen (nhjo@itu.dk)\\ Jacob Benjamin Cholewa (jbec@itu.dk)\\ Jakob Merrild (jmer@itu.dk)\\ Mathias Kindsholm Pedersen (xxxx@itu.dk)}

\begin{document}

\maketitle
\newpage
\tableofcontents

\chapter{Introduction}

\section{Revision History}
\begin{center}
\begin{tabularx}{\textwidth}{|l|l|l|X|}
\hline
\textbf{Version} & \textbf{Edited by} & \textbf{Date} & \textbf{Description} \\
\hline
1.0 & nhjo & 05-02-2014 & Initial Version \\
\hline
1.1 & nhjo & 11-02-2014 & Non-functional requirements added in section 2.4 \\
\hline

\end{tabularx}
\end{center}

\subfile{tex/businessCase.tex}

\chapter{Proposed System}

\section{Overview}
The proposed system is to handle different types of media files (e.g. books, video, sound or images). It must be extendable, such that any given client can upload and search for the most common types of media.

The systems functionality is aimed for anyone that uses their computer as a media center. This is, users that has a collection of books, video-, sound- or imagefiles on their computer or mobile devices.

\section{Scope of the system}

Since our proposal is a full scale rental system, normally you would deal with payment. In our case this is out of scope. Also since every user is able to upload any material, there might also be  issues with infringement of copyright. It is also decided that this is out of the systems scope.

\section{Functional Requirements}

\begin{itemize}
\item Users must be able to register or create a new account, read, update and delete  account information
\item Users must be able to login and logout
\item Admins must be able to add new media, read, update and delete media information. The display of the media should provide information such as the thumbnail image, category (for search), and analytic information (recent searches)
\item The system must support media file types in a genric way
\item Users must be able to search for media files
\item Users must be able to rent and download media (without payment)
\item The system must support at least to types of streamable media
\end{itemize}

\section{Non-functional Requirements}

\subsection{Usability}

\begin{itemize}
\item The client must have an intuitive user interface, such that a novice user must be able to use basic functionality such as creating a user, searching for media and purchasing media files within 2 minutes without reading any tutorials beforehand.
\end{itemize}

\subsection{Reliability}

\begin{itemize}
\item The client must be available at all times, given that the user is online. 
\item If the connection to the service endpoint is lost for any reason, the client must not crash. \item In case of failure the client must provide extensive error messages, such that the user can understand and react to it accordingly.
\end{itemize}

\subsection{Performance}

\begin{itemize}
\item The client must be optimized for fast response time. The user must not experience a delay of more than 5 seconds on any operation, assuming that the internet connection is not the bottleneck.

\item The client should support at least 100 concurrent users. 
\end{itemize}
\subsection{Supportability}

\begin{itemize}
\item Developers must be able to extend the functionality of the client without talking to the original developer. This requires that the code is well written and documented. Such extensions might require a temporary shutdown of the web service.
\end{itemize}

\subsection{Implementation}
\begin{itemize}
\item The client is developed in ASP.NET and is accessible through a web browser.
\item System requirements


\begin{tabular}{| l | l | }
\hline
 Execution environment & Webkit2+ browser \\ \hline
 Processer & 1.4 GHz Scorpion or equivalent \\ \hline
 Memory & 512mb RAM  \\ \hline

\end{tabular}

\item For testing purposes it is required that the code is consistent, unambigous and well documented.
\end{itemize}

\subsection{Interface}

\begin{itemize}
\item {\color{red}What standards in use by the client should be supported by the system?}
\end{itemize}
\section{System Model}

\subsection{Scenarios}

\chapter{Design and Architecture}

\chapter{User Manual}

\chapter{Test Strategy}
All developers write their own unit tests \\
Integration testing is done by a third developer

\chapter{Test}

\chapter{Appendix}


\end{document}