\documentclass[../report.tex]{subfiles}

%As the enumerable can't continue across two seperate subfiles the \documentclass and \begin \end{document} lines must be commented out when commiting changes to this file.

\begin{document}

\label{sec:Functional Requirements}


\subsubsection {Search}

\begin{enumerate}[label=\textbf{FR-\twodigits*}]

	\item All \textit{End Users} must be able to initiate a search by providing a keyword or key-phrase.
	\item The keyword or key-phrase must be matched with \textit{Media Items} on title and \textit{Uploader}.
	\item The \textit{End User} must be presented with a range of all matches.
	\item The \textit{End User} must be able to request the next range of matches as long as there are more matches to show.
	\item Each match must include a link to a detailed page about the \textit{Media Item}.
	\item Matches must be grouped by \textit{Media Type}. 
\end{enumerate}	
			
\subsubsection{Create account}

\begin{enumerate}[label=\textbf{FR-\twodigits*}, resume]
	\item An \texttt{Anonymous User} must be able to create an \textit{Account}.
	\item To create an \textit{Account} the \texttt{Anonymous User} must provide a desired username and password.
	\item Usernames must be unique with case insensitive matching. \label{FR-CA.3}
	\item A \texttt{Anonymous User} must be given an alert if the desired username is unavailable.
	\item A username must consist of between 1 and 20 characters.
	\item A username must only consist of alphanumeric characters (a-zA-Z0-9).
	\item A password must consist of between 1 and 50 characters. 
	\label{FR-CA.6}
	\item A password must not contain any whitespace characters. \label{FR-CA.7}
	\item If requirements \ref{FR-CA.3} - \ref{FR-CA.7} are not met a warning must be displayed to the \texttt{Anonymous User}.
\end{enumerate}
	
\subsubsection {Login}
	
\begin{enumerate}[label=\textbf{FR-\twodigits*}, resume]
	\item An \texttt{Anonymous User} who has already created an \textit{Account} must be able to login to \textit{The System} providing a registered username and password pair.
	\item If the username and password pair is not matched an error message must be displayed to the \texttt{Anonymous User}. 
\end{enumerate}
		
\subsubsection {Manage account}

\begin{enumerate}[label=\textbf{FR-\twodigits*}, resume]
	\item A logged-in \textbf{User} must be able to edit all \textit{Account Information} on his own \textit{Account} excluding username.
	\item An \textbf{Admin} must be able to edit all \textit{Account Information} of all \textit{Accounts} excluding usernames.
	\item Changes to a \textbf{User's} password must still satisfy requirement \ref{FR-CA.6} and \ref{FR-CA.7} \label{FR-MA.2}
	\item A warning must be displayed to the \textbf{User}/\textbf{Admin} if requirement \ref{FR-MA.2} is not met.	
\end{enumerate}
		
\subsubsection {Logout}
\begin{enumerate}[label=\textbf{FR-\twodigits*}, resume]
	\item A logged-in \textbf{User} must be able to logout.
	\item After logout, content only visible to logged-in \textbf{Users} must not be displayed.
\end{enumerate}
	
\subsubsection {Media Item Information} \label{FR-Media}

\begin{enumerate}[label=\textbf{FR-\twodigits*}, resume]
	\item A \textit{Media Item} must have a title.
	\item A \textit{Media Item} must have a description.
	\item A \textit{Media Item} must have a price.
	\item A \textit{Media Item} must have a Thumbnail Image.
	\item A \textit{Media Item} must have an owner.
	\item A \textit{Media Item} must have a type.
	\item A \textit{Media Item} must have a file extension.
	\item A \textit{Media Item} must be able to have keyword tags.
	\item A \textit{Media Item} must be able to have a genre.
	\item A \textit{Media Item} must be able to have either a track length, a runtime or a number of pages.
	\item A \textit{Media Item} must be able to have an author, a director or an artist.
	\item A \textit{Media Item} must be able to have cast members.
	\item A \textit{Media Item} must be able to have a release date.
	\item A \textit{Media Item} must be able to have a language.
	
	\item A \textit{Media Item} must be either available for purchase or unavailable for purchase.
\end{enumerate}

\subsubsection {Uploading Media Items}

\begin{enumerate}[label=\textbf{FR-\twodigits*}, resume]
	\item A logged-in \textbf{User} must be able to upload \textit{Media Items} to the system.
	\item When uploading a \textit{Media Item}, associated \textit{Media Item Informations} must satisfy requirements specified in subsection \ref{FR-Media}.
	\item If an upload is not successfully completed, no information about the \textit{Media Item} must be stored.
	\item If an upload is successful an acknowledgement must be displayed to the \textbf{User}.
	\item If an upload is unsuccessful an error message must be displayed to the \textbf{User}. 
\end{enumerate}

\subsubsection {Purchase Media Items}

\begin{enumerate}[label=\textbf{FR-\twodigits*}, resume]
	\item A \textbf{User} must be able to purchase a \textit{Media Item} which is available for purchase provided he has not uploaded it himself or  purchased it previously.
\end{enumerate}

\subsubsection {Downloading Media Items}

\begin{enumerate}[label=\textbf{FR-\twodigits*}, resume]
	\item A \textbf{User} must be able to download \textit{Media Items} which he has purchased provided they have not been deleted by an \texttt{Admin}.
	\item A \textbf{User} must be able to download \textit{Media Items} which he has uploaded himself provided they have not been deleted by an \texttt{Admin}.
	\item An \textbf{Admin} must be able to download all \textit{Media Items}.
\end{enumerate}
		
\subsubsection {Rating Media Items} \label{FR-RatingMedia}

\begin{enumerate}[label=\textbf{FR-\twodigits*}, resume]
	\item A \textbf{User} must be able to rate \textit{Media Items} which he has purchased on a scale from 1 to 10 with 1 being the lowest rating and 10 being the highest rating.
\end{enumerate}

\subsubsection{Editing Media Item Information}

\begin{enumerate}[label=\textbf{FR-\twodigits*}, resume]
	\item A \textbf{User} must be able to edit the information about \textit{Media Items} which he has uploaded himself provided that all requirements in subsection \ref{FR-Media} are met.
	\item An \textbf{Admin} must be able to edit the information about any \textit{Media Item} provided that all requirements in subsection \ref{FR-Media} are met.
\end{enumerate}
			
\subsubsection {Details Page}

\begin{enumerate}[label=\textbf{FR-\twodigits*}, resume]
	\item The \textit{Media Item} details page must include information about the \textit{Media Item} as specified by the requirements in subsection \ref{FR-Media}.
	\item The \textit{Media Item} details page must provide information about the average rating of the \textit{Media Item} provided that it has been rated at least once.
	\item The \textit{Media Item} details page must provide information about the number of times the \textit{Media Item} has been rated.
\end{enumerate}
			
\end{document}