%\documentclass[../report.tex]{subfiles}

%As the enumerable can't continue across two seperate subfiles the \documentclass and \begin \end{document} lines must be commented out when commiting changes to this file.

%\begin{document}

\noindent

\subsubsection{Read}
\begin{enumerate}[label=\textbf{FR-\twodigits*}, resume]

\item The \textit{ShareIt Back End} must be able to provide \textit{Media Item Information} about a specific \textit{Media Item}.

\item The \textit{ShareIt Back End} must be able to provide a computed average rating of a \textit{Media Item}.

\item The \textit{ShareIt Back End} must be able to provide the amount of ratings given to a \textit{Media Item} if it has been rated at least once.

\item The \textit{ShareIt Back End} must be able to provide a list of promoted \textit{Media Item}s for each \textit{Media Type} individually.

\item The \textit{ShareIt Back End} must be able to provide \textit{Media Item}s in a requested range, grouped by \textit{Media Type}, filtered by a search query.

\item The \textit{ShareIt Back End} must be able to provide \textit{Media Item}s in a requested range, of specific \textit{Media Type} sorted in alphabetical order.

\item The \textit{ShareIt Back End} must be able to validate a login request.

\item The \textit{ShareIt Back End} must be able to notify the \textit{Client} when a login request fails.

\item The \textit{ShareIt Back End} must be able to transfer a \textit{Media Item} to whoever requests it provided that they have access rights to said \textit{Media Item}.

\item The \textit{ShareIt Back End} must be able to provide \textit{Account Information} about a specific \textit{Account}.

\item (S) The \textit{ShareIT Back End} must be able to provide a list of the 10 most purchased \textit{Media Items} in a given timespan

\item (S) The \textit{ShareIT Back End} must be able to provide a list of the 10 most viewed \textit{Details page}s of \textit{Media Items} in a given timespan

\item (S) The \textit{ShareIT Back End} must be able to provide a count on how many times a \textit{Media Item} has occurred in a search result as index 9 or higher index 0 being the first hit. 

\end{enumerate}

\subsubsection{Create}
\begin{enumerate}[label=\textbf{FR-\twodigits*},resume]

\item The \textit{ShareIt Back End} must be able to create new \textit{Account}s containing the information specified in the request.

\item The \textit{ShareIT Back End} must add a unique ID to an \textit{Account} when storing it.

\item Usernames must be unique with case insensitive matching.

\item A username must consist of between 1 and 20 characters.

\item A username must only consist of alphanumeric characters (a-zA-Z0-9).

\item A password must consist of between 1 and 50 characters. 

\item A password must not contain any whitespace characters.

\item The \textit{ShareIT Back End} must be able to receive a \textit{Media Item} file along with any supported types of \textit{Media Item Information} and add it to the collection of stored \textit{Media Items}'s.

\item When the \textit{ShareIT Back End} stores a new \textit{Media Item} each piece of \textit{Media Item Information} must be given a unique ID.

\item When receiving a \textit{Media Item} file the \textit{ShareIT Back End} must add a Media URL Link to the \textit{Media Item}s \textit{Media Item Information} and store the file in the location specified by the Media URL Link.

\item Received \textit{Media Item} files must be accompanied by a Type and a File Extension in order to be stored.

\item The \textit{ShareIT Back End} must add a unique ID to a \textit{Media Item} when storing it.

\item \st{The \textit{ShareIt Back End} must be able to associate an \textit{Account} with a \textit{Media Item}.} %MUST BE DELETED. ALL REFERENCES TO THE FUNCTIONAL REQUIREMENTS WITH HIGHER ID THAN THIS MUST BE UPDATED

\item Associations between \textit{Account}s and \textit{Media Item}s must include a value from 1-10 representing a rating.

\item The \textit{ShareIt Back End} must be able to associate a \textit{Media Item} with an \textit{Account} as \textit{Buyer}.

\item The \textit{ShareIt Back End} must be able to associate a \textit{Media Item} with an \textit{Account} as \textit{Uploader}.
\end{enumerate}

\subsubsection{Update}
\begin{enumerate}[label=\textbf{FR-\twodigits*},resume]

\item The \textit{ShareIt Back End} must be able to update \textit{Account Information} provided that the \textit{User} sending the request has access rights to do so.

\item The \textit{ShareIt Back End} must be able to update \textit{Media Item Information} provided that the \textit{User} sending the request has access rights to do so.
\end{enumerate}

\subsubsection{Delete}
\begin{enumerate}[label=\textbf{FR-\twodigits*},resume]

\item The \textit{ShareIt Back End} must be able to remove a \textit{Media Item} including its \textit{Media Item Information} and its associations to \textit{Account}s provided that the \textit{User} sending the request has access rights to do so.

\end{enumerate}

\subsubsection{Access rights}
\begin{enumerate}[label=\textbf{FR-\twodigits*},resume]

\item The \textit{ShareIt Back End} must be able to check whether or not a \textit{User} has access rights to perform a given request.

\item The \textit{ShareIt Back End} must be able to notify the \textit{Client} if a \textit{User} sends a request which he does not have access rights to perform.

\item (S) Access rights must restrict access if the associated expiration date is exeeded

\item (S) The \textit{ShareIT Back End} must be able to provide data about when a given \textit{User}'s access rights expires.

\item (S) \textit{The ShareIT Back End} must be able to provide access expiration given a \textit{Media Item} and a \textit{User}

\end{enumerate}

%\end{document}