\documentclass[../report.tex]{subfiles}
\begin{document}

This report will describe the system developed by group 8\footnote{Group 8 consists of the authors of this report} as part of the course \textit{Second Year Project: Software Development in Large Teams with International Collaboration (Spring 2014)} at the IT University of Copenhagen (ITU). The course involves an international collaboration between a group of students from Singapore Management University (SMU) and group 8 from ITU.

This report will be describing the motivation for developing the system through a business case. Following that the proposed system derived from the business case including the requirements will be specified. Subsequently an explanation of the design and architecture of the system and its different layers will be provided. Next a validation of the system including the test strategy and a reflection on the test results will be presented. 

Additionally the collaboration process with the group from SMU will be described. This includes a description of the communication and the difficulties encountered when negotiating the requirements as well as a reflection on the collaboration. Finally the project and the intended learning outcome of the course is reflected upon before a conclusion is given.


%In this report we will describe the system we developed as part of the course \textit{Second Year Project: Software Development in Large Teams with International Collaboration(Spring 2014)} (BNDN). We will do this by first describing the business case for the system i.e. the overall goal of the system. Following that we will describe the system specifications derived from the business case. We will give a description of the system design we chose to fulfil the requirements and a description of how we tested that this was also the case.

%Additionally we will describe the collaboration process with the team from Singapore Management University(SMU). This includes a description of our communication with the SMU team and the difficulties we encountered when negotiating the requirements of services as well as a reflection on the collaboration.

%Finally we will reflect on the project as a whole and on how much we learned when held against the intended learning outcome of BNDN.
\end{document}
