\documentclass[../report.tex]{subfiles}
\begin{document}

 %Backend must support multiple clients.

\label{sec:Non-functional Requirements}

\subsubsection{Usability}

\begin{enumerate}[label=\textbf{NFR-\twodigits*}]
\item Without prior knowledge of the \textit{ArtShare}, a user must be able to:
	\begin{enumerate}
	\item Create an \textit{Account} within 5 minutes
	\item Log in within 2 minutes
	\item Log out within 2 minutes
	\item Update the \textit{Users} own \textit{Account Information} within 2 minutes (starting from the front page, already logged in)
	\item Initiate a search within 2 minutes
	\item Find a specific \textit{Media Item} within 2 minutes
	\item Purchase a \textit{Media Item} within 2 minutes (starting from a \textit{Details Page}, already logged in)
	\item Download a \textit{Media Item} within 2 minutes (starting from the relevant \textit{Details Page}, already logged in, having already purchased the \textit{Media Item})
	\item Rate a \textit{Media Item} within 2 minutes (starting from the relevant \textit{Details Page}, already logged in, having already purchased the \textit{Media Item})
	\item Upload a \textit{Media Item} within 2 minutes (already logged in)
	\end{enumerate}
\end{enumerate}

\subsubsection{Reliability}

\begin{enumerate}[label=\textbf{NFR-\twodigits*}, resume]
\item If the connection to \textit{ShareIt} is lost for any reason, \textit{ArtShare} must not crash. 
\item In case of failure \textit{ArtShare} must provide extensive error messages, such that the \textit{User} can understand what went wrong and react to it accordingly.
\item Corrupt data must not reach the \textit{User} in any way.
\end{enumerate}

\subsubsection{Performance}

\begin{enumerate}[label=\textbf{NFR-\twodigits*}, resume]
\item No more than 5 seconds are allowed to pass between \textit{The System} receiving a request and giving a response.
\item \textit{ArtShare} must be able to support at least 10 concurrent users. 
\end{enumerate}

\subsubsection{Supportability}

\begin{enumerate}[label=\textbf{NFR-\twodigits*}, resume]
\item It must be possible to add support for new types of media e.g. photographs.
\item It must be possible to add new functionality and expand upon the existing functionality e.g. adding an advanced search feature.
%\item Extensions might require a temporary shutdown of the web service.
\item The code must be written in such way, that all modules can be tested in isolation.
\end{enumerate}

\subsubsection{Implementation}
\begin{enumerate}[label=\textbf{NFR-\twodigits*}, resume]
\item The client must be developed in ASP.NET and must be accessible through a web browser.
\item Minimum system requirements for \textit{End Users}


\begin{tabular}{| l | l | }
\hline
 Execution environment & Internet Explorer v10+\\
& Google Chrome v31+\\
& Webkit v2.0+\\ \hline
 Processor & 1.4 GHz Scorpion or equivalent \\ \hline
 Memory & 512mb RAM  \\ \hline

\end{tabular}

\item Each unit test must be independent from the others and must test a module in isolation.
\end{enumerate}

%\subsubsection{Interface}

%\begin{enumerate}[label=\textbf{NFR-\twodigits*}, resume]
%\item {\color{red}What standards in use by the client should be supported by the system?}
%\end{enumerate}

\end{document}
