%\documentclass[../report.tex]{subfiles}
%\begin{document}

\subsubsection{Actors}
\label{sec:Actors}
\begin{itemize}
\item \textbf{Admin} \\
The Admin is a user with extended access rights to all content. 
\item \textbf{Anonymous User}\\ 
The Anonymous User is an anonymous \textit{End User} of \textit{The System}. This actor is not able to use all functionality of \textit{The Syetem}. Only browsing the content is allowed
\item \textbf{User} \\
The User is a registered and identified \textit{End User} of \textit{The System}. He has an \textit{Account} which he is logged into. This actor is allowed to do more than the Anonymous User. This includes uploading, purchasing and rating content and managing account information and content uploaded by the User himself.
\end{itemize}

\subsubsection{User Stories}
\label{sec:User Stories}
\begin{itemize}
\item \textbf{UploadContent} \\
John is an \texttt{Anonymous User} of \textit{ArtShare}. He wants to upload "The best day of my life", a movie he has made, so he can make some money from it. In order to be able to do so he must create an \textit{Account} in order to become a \texttt{User}. He creates an \textit{Account} called John33 which he logs into. John33 finds the movie file he wants to upload and enters information about it into \textit{The System}. He then uploads the movie.
\item \textbf{PurchaseAndDownloadContent} \\
Robert is an \textit{Anonymous User} of \textit{ArtShare}. He wants to purchase "War and Peace" as an ebook. He uses the search function to find the ebook he is looking for. In order to be able to purchase the ebook he must log in. Robert already has an \textit{Account} called Robbie93 so he logs in as Robbie93. Robbie93 purchases the ebook and downloads it.
\item \textbf{RateContent} \\
Daniel54 is a registered \textit{ArtShare} \texttt{User}. He has previously purchased and listened to the Pink Floyd song "Money". He thought it was a great song and he wants to let the other users of \textit{ArtShare} know about this. He finds "Money" using the search function. He then uses the rating system to give it a high rating.
\item \textbf{ManageUploadedContent} \\
Bob1970, a registered \texttt{User} of \textit{ArtShare}, notices that he made a spelling error in the title of the music track he just uploaded. He changes the title from "Parise the Lord" to "Praise the Lord" and saves the changes.
\item \textbf{ManageAccount} \\
Kelly89 is a registered \texttt{User} of \textit{ArtShare}. She has not yet added anything to her \textit{Account Information}. She now wants to add her e-mail address so that other users can contact her. She updates her e-mail address and saves the changes.
\item \textbf{DeleteContent} \\
Anna, an \texttt{Admin} of \textit{ArtShare}, has found a \textit{Media Item} without content. Anna deletes the \textit{Media Item} to avoid unsatisfied users.
\end{itemize}

%\end{document}