\documentclass[../report.tex]{subfiles}
\begin{document}

\subsection{Multiple services}
We decided to make multiple services instead of one to maintain a high cohesion in the different services. The idea is that it is very clear what the responsibility of each service is - both for the users of the service (\textit{Client}s) and for other developers. This makes it easy for the \textit{Client}s to figure out which service to use and it will make it more convenient to find specific operations instead of having to look through one bloated service. Multiple services instead of one also allows for separate, dedicated front-ends that would target just certain parts of the whole system. 

It introduces a problem with our Data Transfer Objects which are not shared between the different services though. This will be described in section \textcolor{red}{?? Update this reference to DTO section}. 

\subsection{Service responsibilities}
As mentioned in the previous section, there are five different services, which are responsible for different parts of the system. 

The \texttt{AccessRightService} is responsible for all operations on access rights. This includes making new admins, creating new access rights when a user purchases a \textit{Media item}, editing expiration dates, deleting access rights and getting purchase or upload histories of users. 

The \texttt{AuthService} handles all authentications of users and clients. This is used keep control of which \textit{Client}s use the services and to make sure that the users of the different clients exists in the system. The service is also able to check if a given user is admin on a given client.

The \texttt{MediaItemService} handles all actions that can be performed on \textit{Media item}s. These actions involve getting a specific media item, getting multiple media items or getting multiple media items of a specific type. Searching is also handled here, and again this can be performed on all media items or on media items of a specific type if desired. Besides from getting and searching, the service handles updates on media items, deletions of media items and ratings on media items.

The \texttt{TransferService} is responsible for uploading and downloading data. It allows users to download the data of a specific media item and to upload a media item with its information and its data. It is also responsible for uploading thumbnail images and associating these with media items.

The \texttt{UserService} handles all user related actions. This includes creating \textit{Account}s, getting \textit{Account Information}, updating \textit{Account Information}, deleting \textit{Account}s and getting all users. 

\end{document}